---
title: "Coding Assignment Part 2"
author: "Tobias Holden"
date: '2023-04-29'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(data.table)
```

Read in cleaned data from Part 1

```{r}

```

Aggregate the count, mean, and standard deviation of Var 1 and Var 3 on each Day for a given Site

```{r}

```

Use mutate to add upper and lower 95% prediction intervals around the daily mean of Var1 and Var3 at each Site  (mean ± 1.96 * sd ÷ √n)

```{r}

```

Use `ggplot2` to produce plots of the data:

* Day on the x-axis, Var# on the y-axis  
* Separate lines and colors for each dependent variable (Var 1 and Var 3)  
* Separate facets for each Site  
* An informative title, labels, legend, color palette etc.  
  * You don't need to spend much time on plot appearance for this for this assignment, but it is an important part of communicating our findings  
  
```{r}

```


Save your plot(s) as `.png` file(s) in `project_dir/` with a descriptive file name (ex. "Variables1-2_by_Site.png")


```{r}

```



