---
title: "Coding Assignment Part 2"
author: "Tobias Holden"
date: '2023-04-29'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(data.table)
```

Read in cleaned data from Part 1

```{r}
df <- fread('output_cleaned.csv')
```

Aggregate the count, mean, and standard deviation of Var 1 and Var 3 on each Day for a given Site

```{r}
df %>%
  select(Day, Site, Var1, Var3) %>%
  gather(key="variable", value="value", 3:4) %>%
  group_by(Day,Site,variable) %>%
  summarize(n=n(),
            average=mean(value),
            std_dev = sd(value)) -> df
```

Use mutate to add upper and lower 95% prediction intervals around the daily mean of Var1 and Var3 at each Site  (mean ± 1.96 * sd ÷ √n)

```{r}
df %>%  
  rowwise() %>%
  mutate(upperCI = average + 2.56*std_dev/n,
         lowerCI = average - 2.56*std_dev/n) -> df
```

Use `ggplot2` to produce plots of the data:

* Day on the x-axis, Var# on the y-axis  
* Separate lines and colors for each dependent variable (Var 1 and Var 3)  
* Separate facets for each Site  
* An informative title, labels, legend, color palette etc.  
  * You don't need to spend much time on plot appearance for this for this assignment, but it is an important part of communicating our findings  
  
```{r}
df %>%
  ggplot(aes(x=Day, color=variable, fill=variable)) + 
    facet_wrap(~paste("Site",Site), scales="fixed") +
    geom_path(aes(y=average,
                  group=variable)) +
    geom_ribbon(aes(ymin = lowerCI, 
                    ymax=upperCI, 
                    group=variable), 
                alpha=0.5) + 
  ylab("mean value (with 95% CI)") + 
  labs(color=NULL, fill=NULL)+
  theme_minimal() +
  scale_fill_brewer(palette="Set2", direction = 1) +
  scale_color_brewer(palette="Set2", direction = 1)-> my_plot

my_plot
```


Save your plot(s) as `.png` file(s) in `project_dir/` with a descriptive file name (ex. "Variables1-2_by_Site.png")


```{r}
ggsave(filename='Variables1-2_by_Site.png', 
       plot = my_plot)
```



